Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Grammar

\begin{table}[h]
%\vspace{-0.2cm}
\begin{center}
\begin{tabular}{cc} \\ 
flight & matches \\ \hline
0 & (0,1) (2,3) (4,5)  \\
1 & (0,2) (4,6) (1,5)  \\
2 & (2,6) (0,5) (1,3)  \\
3 & (5,6) (0,3) (1,4)  \\
4 & (3,5) (1,6) (2,4)  \\
5 & (3,6) (0,4) (2,5)  \\
6 & (3,4) (1,2) (0,6)  \\ \hline
\end{tabular}
\end{center}
\caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights. Skippers are numbered 0 to 6. Note that the order of skippers within a flight are significant as is position within a match (port or starboard). This schedule is the result of stages 1 and 2, and has yet to be renumbered and oriented (stages 3 and 4)}
\label{tab1}
\end{table}

>>>>

\begin{table}[h]
%\vspace{-0.2cm}
\begin{center}
\begin{tabular}{cc} \\
flight & matches \\ \hline
0 & (0,1) (2,3) (4,5)  \\
1 & (0,2) (4,6) (1,5)  \\
2 & (2,6) (0,5) (1,3)  \\
3 & (5,6) (0,3) (1,4)  \\
4 & (3,5) (1,6) (2,4)  \\
5 & (3,6) (0,4) (2,5)  \\
6 & (3,4) (1,2) (0,6)  \\ \hline
\end{tabular}
\end{center}
\caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
Skippers are numbered 0 to 6. Note that the order of skippers within a flight
is significant, as is position within a match (port or starboard). This
schedule is the result of stages 1 and 2, and has yet to be renumbered and
oriented (stages 3 and 4).}
\label{tab1}
\end{table}
